\LARGE \bf A Pipeline to Assemble Near-Accident Footage Datasets

### 2020-10-07 paper.tex
combine intro and background/preliminary sections

In the advent of connected vehicles and autonomous transportation, equipping consumer vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems can be prohibitively expensive.
Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers and might not easily be affixed to their vehicles (maybe not true).
We note that front-facing dash-cams have become increasingly affordable and prevalent as a means to capture a driver’s perspective leading up to the event of a potential collision.
This has led to the creation of many online communities to share such videos.
We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{BACKGROUND / PRELIMINARY}
\todo{write the background / preliminary} \\
introducing basic ideas to readers. why is the annotation pipeline important (how was the annotation toolbox developed) - use separate subsections

\todo{Work in progress}

Dash-cams are cheap video cameras that can be mounted a car's dashboard or windshield to continuously save a recording of a driver's perspective to an internal memory card.
Exceptional events recorded by the dashcam such as collisions and crashes are often uploaded and shared to popular social media websites and video repositories such as Reddit, Youtube, and Imgur and are typically tagged with a closely related set of key terms.
The pipeline uses web-scraping techniques to fetch the video data from these websites, along with a set of video metadata, describing the video's contents.
We use this data, in combination with the manually annotated data in order to create the collision dataset.
\todo{Not sure what else to put here}

>>>>

In the advent of connected vehicles and autonomous transportation, equipping consumer vehicles with the necessary equipment to facilitate high-end automated collision avoidance systems can be prohibitively expensive.
Technologies such as Radar, LIDAR and high-end cameras that are typically used for collision prediction are likely too expensive for most consumers and might not easily be affixed to their vehicles (maybe not true).
On the other hand dash-cams, cheap video cameras that can be mounted a car's dashboard, have become increasingly affordable and prevalent as a means to capture a driver’s perspective.
Typically used for insurance purposes, dash-cams have the added benefit of recording a wide variety of collisions that wouldn't be feasible to simulate. 
This has led to the creation of many online communities to share videos of these rare situations on websites such as Reddit, Youtube, and Imgur.
We propose that this egocentric dash-cam video stream can be leveraged by computer vision systems to act as an affordable and commonplace sensor for automated collision prediction.

@@

The pipeline uses web-scraping techniques to fetch the video data from these websites, along with a set of video metadata, describing the video's contents.
We use this data, in combination with the manually annotated data in order to create the collision dataset.
This combination allows us to take advantage of the wide variety of videos available on the internet, while still having reliable data that has been curated manually.
\todo{Not sure what else to put here}
